---
title: "Ketamine-Assisted Therapy for Methamphetamine Use Disorder (Synthetic RCT)"
subtitle: "Zed R/Python Toolchain Verification -- Task 20"
author: "epi-implement-agent"
date: "2026-04-10"
format:
  html:
    toc: true
    toc-depth: 2
  gfm:
    preview-mode: raw
execute:
  echo: false
  warning: false
---

## Background

This is a verification exercise for Zed's R and Python toolchains on NixOS.
We analyze a synthetic 1:1 randomized controlled trial of Ketamine-Assisted
Therapy (KAT) vs Therapy-As-Usual (TAU) for methamphetamine use disorder,
N=200 participants stratified by baseline severity.

> **Note**: All data are synthetic. No real participants or clinical inference.

## Methods

**Design**: 1:1 stratified RCT, 12-week follow-up.
**Primary outcome**: Abstinence from methamphetamine at 12 weeks (binary).
**Secondary outcomes**: Time to first use (continuous, censored at 84 days),
Addiction Severity Index (ASI) at 12 weeks.
**Primary analysis**: Logistic regression adjusting for severity stratum,
age, sex, and baseline ASI.

## CONSORT Flow

```{r}
#| label: consort-flow
dat <- read.csv("../data/derived/analytic.csv")
cat("Enrolled:            ", nrow(dat), "\n")
cat("Randomized to KAT:   ", sum(dat$arm == "KAT"), "\n")
cat("Randomized to TAU:   ", sum(dat$arm == "TAU"), "\n")
cat("Completed study:     ", sum(dat$completed_study == 1), "\n")
cat("Lost to follow-up:   ", sum(dat$completed_study == 0), "\n")
```

## Table 1: Baseline Characteristics

Generated via base R aggregation (see
`reports/tables/primary_results.txt`). `gtsummary` is unavailable in
this environment.

## Primary Results

Odds ratio (KAT vs TAU) for abstinence at 12 weeks, complete-case analysis:

```{r}
#| label: primary-or
m <- readRDS("../data/derived/models/primary_logistic.rds")
co <- summary(m)$coefficients
ci <- confint.default(m)
arm <- which(rownames(co) == "armKAT")
cat(sprintf("OR = %.2f (95%% CI %.2f-%.2f), p = %.4f\n",
            exp(co[arm, 1]), exp(ci[arm, 1]), exp(ci[arm, 2]), co[arm, 4]))
```

## Secondary Results

- **Time-to-relapse (Cox fallback)**: `survival` package unavailable;
  a log-rank test and exponential-glm fallback were used. See
  `reports/tables/primary_results.txt` for details.
- **ASI at 12 weeks**: Linear regression adjusting for the same covariates.

## Sensitivity Analyses

See `reports/tables/sensitivity_results.txt`. Five sensitivity scenarios were
run: complete case (primary), per-protocol, single-imputation, and worst-case
/ best-case tipping-point bounds.

## Limitations

1. Synthetic data only; effect sizes are pre-specified, not estimated.
2. Cox regression replaced by log-rank + exponential glm fallback because
   the `survival` R package is not installed.
3. Multiple imputation replaced by mean/mode single imputation because
   `mice` is not installed.
4. Quarto rendering is disabled because Quarto is not installed; this
   document is maintained as a `.qmd` source plus a Markdown mirror
   (see `05_consort_report.md`).

## Configuration Gaps

See `logs/config_gaps.md` for the full list of missing packages and the
recommended NixOS remediation snippets.
